### 2019-11-05 thesis/txt/5-study.tex
new chapter 6: discussion, start on results for CTS, replotting quite some things

\chapter{Empirical Comparison Study}
\label{sec:study}
To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build logs we evaluated our implementation of those techniques on the \emph{Failing Build Log Data Set}.
This chapter describes our study design, the analysis of the study results and threats to the validity of our conclusions.
The analysis of the study results first focusses on each of the three techniques and describes how each one performs best.
Later we compare them against each other and describe their trade offs against each other.
This chapter answers our second research question and its subquestions:
\begin{simplebox}{Research Questions}
\begin{itemize}
  \item[\textbf{RQ2:}] When are PBE, TS, and SKWS suited to retrieve information from CI build logs?
  \item[\textbf{RQ2.1:}] How many examples do PBE, TS, and SKWS need to perform best?
  \item[\textbf{RQ2.2:}] How accurate are the retrievals of PBE, TS, and SKWS?
  \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE and TS need to be for the techniques to be applicable?
\end{itemize}
\end{simplebox}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/study-design.pdf}
	\caption{Study Design of our technique comparison study}
	\label{fig:study}
\end{figure}

@@

For each of our evaluation runs we measure the desired vs. actual output lines of the chunk retrieval.
The desired output is given by the output of the test I/O example, which acts as the oracle for our evaluation.
From this we obtain true/false positives/negatives and calculate precision, recall and accuracy, which we use to answer \textbf{RQ2.2}.
We register the number of examples used as configuration for each run to answer \textbf{RQ2.1} and their structural categories to answer \textbf{RQ2.3}.

@@

\section{Analysis}
This section presents the evaluation results for PBE, CTS and KWS separately and discusses under which circumstances these techniques yield best results.
Afterwards it compares the three techniques with each other and RLR as baseline.
The section concludes with recommendations on which technique is suited for different situations.

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
		\caption{Success of Chunk Retrieval Runs with PBE}
		\label{fig:failure-reason-PBE}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
		\caption{Success of Chunk Retrieval Runs with PBE Compared with Category Count}
		\label{fig:failure-reason-categorycount-PBE}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-extraction-result-PBE.pdf}
		\caption{Precision of PBE Chunk Retrieval Results Compared with Example Count}
		\label{fig:precision-extraction-result-PBE}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-singlecategory-swarm-PBE.pdf}
		\caption{Precision of PBE Chunk Retrieval Compare with Example Count and Category Singularity}
		\label{fig:precision-singlecategory-swarm-PBE}
	\end{minipage}
\end{figure}
\subsection{Regular Expression Program Synthesis by Example (PBE)}
Out of the 400 runs in our evaluation, 5 runs per each of the 80 example sets, PBE extracted all the desired lines in 138 cases.
Figure \ref{fig:failure-reason-PBE} shows that in 89 cases a program was successfully synthesized, though in 59 cases the synthesized program yielded no output at all.
In 30 cases the synthesized program did not extract all of the desired lines, though still had an average recall of 28\%.
In 173 cases the PROSE program synthesis could not synthesize a singular regular expression program that satisfies all of the configuring examples.

Figure \ref{fig:failure-reason-categorycount-PBE} shows that the success of the program syntesis algorithm highly depends on the structural categories present in the configuring examples.
Programs could only be synthesized if at maximum two categories were present.

More than three examples yield no improvement in the precision of PBE chunk retrieval, as you can see in Figures \ref{fig:precision-extraction-result-PBE} and \ref{fig:precision-singlecategory-swarm-PBE}.

% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-PBE.pdf}
% 		\caption{Successful Extractions per Number of Examples for PBE}
% 		\label{fig:success-examples-pbe}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-PBE.pdf}
% 		\caption{Precision of Extractions per Number of Examples for PBE}
% 		\label{fig:precision-pbe}
% 	\end{minipage}
% \end{figure}
% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-PBE.pdf}
% 		\caption{Precision of PBE Extractions by CategoryCount}
% 		\label{fig:precision-categorycount-examplecount-pbe}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
% 		\caption{Reasons for PBE Runs to Fail}
% 		\label{fig:failure-reason-pbe}
% 	\end{minipage}
% \end{figure}

% This section addresses the results produced by the PBE technique in our study.
% We start by comparing success rate and precision for different example counts and showing the influence of example categories.
% Next we go into detail in which cases pbe fails
% \subsubsection{Success-Rate}
% \subsubsection{Precision}
% \subsubsection{Example Categories}
% \subsubsection{Specific Failure Reasons}
% \todo{FAILURE REASON AGAINST EXAMPLE CATEGORIES}
% \subsection{Successful Extractions}
% successful is interpreted by us as: all lines that were desired (within our oracle) were also extracted during the test

% Figure \ref{fig:success-all} shows how successful the four different tecnhiques were in our study.
% Figure \ref{fig:success-examples-pbe} shows that the success rate for PBE decreases with increasing example count for pbe. Section \ref{TODO ref to pbe section} explains in more detail whi this fails
% Figure \ref{fig:success-examples-ts} shows that the success rate for TS varies but stays roughly the same for different example counts
% Figure \ref{fig:success-examples-skws} shows that the success rate for KWS varies but stays roughly the same for different example counts
% Figure \ref{fig:success-examples-pbe} shows that

\subsection{Common Text Similarity (CTS)}

>>>>

\chapter{Empirical Comparison Study}
\label{sec:study}
To investigate when PBE, CTS and KWS are suited to retrieve chunks from CI build logs we evaluated our implementation of those techniques on the \emph{Failing Build Log Data Set}.
This chapter describes our study design and presents the results of the study.
The analysis of the study results first focusses on each of the three techniques and later we compare them against each other.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth, clip]{img/study-design.pdf}
	\caption{Study design of our technique comparison study}
	\label{fig:study}
\end{figure}

@@

For each of our evaluation runs we measure the desired vs. actual output lines of the chunk retrieval.
The desired output is given by the output of the test I/O example, which acts as the oracle for our evaluation.
From this we obtain true/false positives/negatives and calculate precision, recall and accuracy, which we use to answer \textbf{RQ2.2}.
We register the number of examples used as configuration for each run to answer \textbf{RQ2.1} and their structural categories to answer \textbf{RQ2.3}.
\todo{mention / explain retrival size facto}

@@

\section{Results}
This section presents the evaluation results for PBE, CTS and KWS separately.
Afterwards it compares the three techniques with each other and RLR as baseline.

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
		\caption{Results of chunk retrieval with PBE}
		\label{fig:failure-reason-PBE}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
		\caption{Results of chunk retrieval with PBE for numbers of categories present in configuring I/O examples}
		\label{fig:failure-reason-categorycount-PBE}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-extraction-result-PBE.pdf}
		\caption{Precision chunk retrieval with PBE for increasing count of configuring I/O examples}
		\label{fig:precision-extraction-result-PBE}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}
\subsection{Regular Expression Program Synthesis by Example (PBE)}
Figure~\ref{fig:failure-reason-PBE} shows the results of the PBE runs in our evaluation.
Out of the 400 runs, 5 per each one of the 80 example sets, PBE extracted all the desired lines in 138 cases.
Figure \ref{fig:failure-reason-PBE} shows that in 89 further cases a program was also successfully synthesized, though in 59 cases the synthesized program yielded no output at all.
In 30 cases the synthesized program did not extract all of the desired lines, though still had an average recall of 28\%.
In 173 cases the PROSE program synthesis could not synthesize a singular regular expression program that satisfies all of the configuring I/O examples.

Figure \ref{fig:failure-reason-categorycount-PBE} shows the results of PBE runs compared to the number of categories present in the configuring I/O examples.
It shows that the program synthesis is more likely to succeed when there are few categories present in the configuring I/O examples.
When two categories present, PROSE could not synthesize a program consistent with all configuring I/O examples in most cases.
For three or more categories PROSE could never synthesize a consistent program.

Figure \ref{fig:precision-extraction-result-PBE} compares the precision of the PBE chunk retrieval runs with the count of configuring I/O examples.
For one example there is a high number of empty extraction outputs, meaning that the regular expression synthesized from this one I/O example could not be applied to the test I/O example.
For two or more I/O examples the chunk retrieval is either successful or no consistent program could be synthesized.

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-TS.pdf}
		\caption{Paieya}
		\label{fig:recall-precision-examplecount-TS}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-TS.pdf}
		\caption{nei}
		\label{fig:recall-precision-categorycount-TS}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-TS.pdf}
		\caption{neind}
		\label{fig:contextsizefactor-precision-recall-TS}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

\subsection{Common Text Similarity (CTS)}
Figure \ref{fig:recall-precision-examplecount-TS} presents precision and recall of chunk retrieval using CTS in our study for different numbers of configuring I/O examples.
The count of configuring I/O examples has no visible influence on recall and precision of the chunk retrieval with CTS.

Figure \ref{fig:recall-precision-categorycount-TS} shows the same measurements for different category counts in the configuring I/O examples.
With increasing category count, precision and recall decrease.
Especially for more than three categories present we have no chunk retrieval runs where all desired lines were extracted.

Figure \ref{fig:contextsizefactor-precision-recall-TS} shows the impact of the retrieval size factor on precision and accuracy of chunk retrieval runs with CTS.
The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
The recall ranges

### 2019-11-05 thesis/txt/6-discussion.tex
new chapter 6: discussion, start on results for CTS, replotting quite some things

\begin{document}

\chapter{Introduction}
\plan{finalized, out for review}
Continuous Integration (CI) has become a best practice in software engineering.
Many software projects now use CI~\cite{hilton2016usage,staahl2014modeling,beller2017oops} to detect bugs more easily~\cite{vasilescu2015quality,duvall2007continuous} and improve developer productivity~\cite{miller2008hundred,hilton2016usage} and communication~\cite{downs2012ambient}.
A build on a CI server typically not only compiles and packages the software, but also executes tests~\cite{beller2017oops} and various kinds of static analyses~\cite{zampetti2017open}.

CI builds produce long and verbose build logs~\cite{beller2017oops}, stating the progress and results of the various steps within the build.
The structure of these logs changes greatly from project to project~\cite{staahl2014modeling} as it highly depends on the tools and environment used.
Build logs are a valuable data source. First of all, for developers, who read them to analyze why their build failed or how different stages of the build process perform.
Second, they are valuable for researchers, who can harvest the information contained in the logs --- and their metadata --- to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
However, these two groups can only utilize the information within the build logs if they can adequately retrieve the information relevant to them.

There are different techniques used to retrieve information from CI build logs. Beller et al. use regular expressions to analyze the failure reasons of Ruby and Java Maven build logs from TravisCI~\cite{beller2017oops}.
In general, such regular expressions are developed by looking at a few exemplary build logs and updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
Vassallo et al. wrote a custom parser for Java Maven build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
Recently, Amar et al. greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build~\cite{amar2019mining}.

Currently there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred.
Developers and researches have little support while choosing which technique to use for a retrieval task.
The goal of this thesis is to investigate different information retrieval techniques (IR techniques) and describe under which circumstances we recommend each of the techniques.

We aim to define a model to characterize different IR techniques, as well as the information retrievable from CI build logs.
For our first research question, we analyze which criteria influence the suitability of an IR technique.
We support our assumption by implementing and evaluating three techniques:
\begin{itemize}
  \item regular expression program synthesis from examples using the Microsoft PROSE library (referred to as PBE),
  \item a common text similarity approach (referred to as TS) and
  \item simple keyword search (referred to as SKWS)
\end{itemize}
Our second research question asks in which cases PBE, TS and SKWS are suited to retrieve information from continuous integration build logs. RQ2 is refined into sub-questions along the criteria resulting from RQ1 and compares their instantiations for the three techniques: how many examples a technique needs to perform best, the accuracy of the retrieved output and how structurally diverse the configuring examples can be.
\begin{simplebox}{Research Questions}
\begin{itemize}
  \item[\textbf{RQ1:}] Which criteria influence the suitability of an information retrieval technique for CI build logs?
  \item[\textbf{RQ2:}] When are PBE, TS, and SKWS suited to retrieve information from CI build logs?
  \item[\textbf{RQ2.1:}] How many examples do PBE, TS, and SKWS need to perform best?
  \item[\textbf{RQ2.2:}] How accurate are the retrievals of PBE, TS, and SKWS?
  \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE and TS need to be for the techniques to be applicable?
\end{itemize}
\end{simplebox}
To evaluate PBE, TS and SKWS we create the \emph{Failing Build Logs Data Set}, which encompasses about 800 log files from 80 repositories. Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural position within the log.

\plan{results and conclusions of my work}
Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that PROSE is suitable for retrieval tasks requiring a high precision, ... . Retrieving information by using text similarity of examples is suitable when ... . Simple keyword search is suitable ... .

\paragraph{Our work contributes:}
\begin{itemize}
  \item A model of the retrievable information in CI build logs
  \item A model to characterize information retrieval techniques from CI build logs
  \item A model to characterize use case scenarios for information retrieval from CI build logs
  \item A tool unifying several information retrieval techniques namely:
        \begin{itemize}
          \item regular expression program synthesis from examples using the Microsoft PROSE library (PBE),
          \item a common information retrieval approach using text similarity (TS), and
          \item a simple keyword search approach (SKWS)
        \end{itemize}
  \item The \emph{LogCollector}, a tool to gather build logs from Travis CI
  \item A validated data set of about 800 logs from failed Travis CI builds labeled with:
        \begin{itemize}
          \item the substring of the log describing the reason the build failed,
          \item keywords developers would use to search for these descriptions of the build failure reason, and
          \item a categorization of the retrievals according to their structural position within the build log
        \end{itemize}
  \item An evaluation of our model for the three implemented information retrieval techniques \todo{describe \emph{what} we look for with this evaluation}
  \item An extendable scheme supporting decision on (our three) information retrieval techniques relative to a given use case scenario
\end{itemize}

This thesis first presents an overview of the related research, spanning from CI research, build log analysis and augmentation, and common system log processing over information retrieval techniques to program synthesis by examples.
Next, chapter \ref{sec:models} presents our models for information retrieval techniques, use case scenarios for such techniques and retrievable information from CI build logs. It also introduces the three techniques, we focus on during our research evaluation.
Chapter \ref{sec:data-set} describes the creation of our \emph{Failing Build Logs Data Set} collected from failed Travis CI build logs and the labeling as well as the validation process.
Following, Chapter \ref{sec:implementation} our implementation of the three chosen information retrieval techniques and the usage of our unified information retrieval tool.
This tool is also used for the evaluation study of our models described in Chapter \ref{sec:study}. There we also describe the resulting instantiation of our recommendation model for regex program synthesis, text similarity, and keyword search.
Lastly, we conclude and give an overview of further research opportunities in Chapter \ref{sec:conclusion}.
\end{document}

>>>>

\begin{document}
\chapter{Discussion}

This chapter answers our second research question and its subquestions:
\begin{simplebox}{Research Questions}
\begin{itemize}
  \item[\textbf{RQ2:}] When are PBE, TS, and SKWS suited to retrieve information from CI build logs?
  \item[\textbf{RQ2.1:}] How many examples do PBE, TS, and SKWS need to perform best?
  \item[\textbf{RQ2.2:}] How accurate are the retrievals of PBE, TS, and SKWS?
  \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE and TS need to be for the techniques to be applicable?
\end{itemize}
\end{simplebox}

\section{wip: best usage of single techniques}
\subsection{wip: best usage of PBE}
\subsection{wip: best usage of CTS}
\subsection{wip: best usage of KWS}

\section{wip:when to choose which technique}

\end{document}
